---
title: "Retina"
author: "Lars Schmitz and Brian Cohn"
date: "February 12, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading helper functions

You will need a few helper functions to plot a retina map.

```{r, warning=FALSE, message=FALSE}
source("helper_functions.r")
source("beta_functions.r")
temp_dir <- tempdir(check = TRUE)
```


## Creating a temporay directory for storage of ojects

[explain why a temp dir is useful]

```{r}
temp_dir <- tempdir(check = TRUE)
```


## Loading required data

Here is what you need:
[list]

```{r}
# outline of the retina wholemount
roi_path <- "sample_retina/outline.roi"

# coordinates of datapoints collected
measurements <- fread("sample_retina/datapoints.csv")

#3 outlines of the optic nerve head (and falciform process if present)
falciform_coords_raw <- fread("sample_retina/falciform.csv") #NOTE: RENAME THIS OBJECT?
```

## Defining tears of the retina wholemount

It is necessary to identify the tears in the wholemount before the retistruction.

```{r, warning=FALSE, message=FALSE}
#use this plot to define the tears
save_outline_indices_plot(load_roi(roi_path), measurements, "output/outline_coordinates.pdf")
#we need to show this plot
```

Now enter the points that define each tear.
Note that each tear is a row: c(middle tear point, before, after). Add commas as necessary.

```{r}
tear_coordinates_dataframe <- rbind(
	c(34,31,35),
	c(5,4,6),
	c(14,11,16),
	c(25,23,27)
	)
```


## Assemble a mark up file

[explain what that means]

```{r}
markup_information <- data.frame(eye_side=as.character("right"), 
                                 nasal_outline_index=NA, 
                                 dorsal_outline_index=8,
                                 phi0=0)# [need annotations]
markup_information$eye_side <- as.character(markup_information$eye_side)

assemble_markup_file(markup_information$eye_side, 
                     temp_dir, 
                     nasal_outline_index=markup_information$nasal_outline_index,
                     dorsal_outline_index=markup_information$dorsal_outline_index, 
                     phi0=markup_information$phi0)
```

## Hold on to your incremental work

Copy files in the temporary directory to hold on to the incremental work you have done so far.

```{r, message=FALSE}
file.copy(roi_path, file.path(temp_dir,"outline.roi"), overwrite=TRUE)
tear_df <- assemble_tear_file(tear_coordinates_dataframe, temp_dir)
```

## Perfom "retistruction" 

[explain wat that means, make reference to Sterratt's work]

```{r, warning=FALSE, message=FALSE}
r_outline <- retistruct.read.dataset(temp_dir) # expect scale bar warning
r_markup <- retistruct.read.markup(r_outline) # make sure there is no P.csv already in the folder [??]
r_reconstructed <- retistruct.reconstruct(r_markup)
# projection(r_reconstructed) DO WE NEED THIS?
```

## Preparing plotting

[explain what we need, why we are doing this]

```{r, warning=FALSE, message=FALSE}
grid_coordinates <- grid_within_bounding_box(load_roi(roi_path)$coords,100)
grid_dt <- generate_projection_data(grid_coordinates, r_reconstructed)
landmarks <- directional_landmarks(grid_dt)

outline_coordinates <- extract_wholemount_outline(load_roi(roi_path))
outline_dt <- generate_projection_data(outline_coordinates, r_reconstructed)

measurement_coordinates <- apply_retistruct_inversion_to_datapoints(measurements,load_roi(roi_path))
measurement_dt <- generate_projection_data(measurement_coordinates, r_reconstructed)

falciform_coordinates <- apply_retistruct_inversion_to_datapoints(falciform_coords_raw,load_roi(roi_path))
falciform_dt <- generate_projection_data(falciform_coordinates, r_reconstructed)
```

## Flatmount plotting

[explain]

```{r}
p <- ggplot() + coord_fixed() + theme_classic()
p <- p + geom_polygon(aes(x,y), data = outline_dt, col="black", alpha=0) # show outline
p <- p + geom_point(aes(x, cyan, col=measurement), data = measurement_dt)  + scale_colour_gradient2()
p <- p + geom_label(aes(x,y,label=name),data=landmarks, alpha=0.5)
p <- p + geom_polygon(aes(x,cyan),data=falciform_dt, alpha=0, col="black")
ggsave("output/flatplot.pdf",p,width=8, height=8)
p
```

## Reconstructed plotting of the hemisphere

[explain]

```{r, warning=FALSE}
# remove the NA's where there were no points
dtt_projected <- na.omit(measurement_dt, cols="azi_x")

#plotting
fit_data <- fit_plot_azimuthal(dtt_projected$azi_x,
                               dtt_projected$azi_y, 
                               z = dtt_projected$measurement,
                               outer_radius = 1.6,
                               spatial_res = 1000,
                               lambda = 0.01,
                               col_levels = 50,
                               contour_levels = 20,
                               extrapolate = FALSE,
                               compute_error = TRUE,
                               eye_diameter = 0,
                               axial_len = 0,
                               falciform_coords = NA)
polygon(falciform_dt$azi_x,falciform_dt$azi_y, col="black")
```


Save plot as PNG file.

```{r, warning=FALSE, message=FALSE}
png("output/my_retina_figure.png", width=1200,height=800)
fit_data <- fit_plot_azimuthal(dtt_projected$azi_x,
                               dtt_projected$azi_y, 
                               z = dtt_projected$measurement,
                               outer_radius = 1.6,
                               spatial_res = 1000,
                               lambda = 0.01,
                               col_levels = 50,
                               contour_levels = 20,
                               extrapolate = FALSE,
                               compute_error = TRUE,
                               eye_diameter = 0,
                               axial_len = 0,
                               falciform_coords = NA)
polygon(falciform_dt$azi_x,falciform_dt$azi_y, col="black")
dev.off()
```

PDF output is cleaner.

```{r, warning=FALSE, message=FALSE}
pdf("output/my_retina_figure.pdf", width=11,height=8.5, useDingbats=FALSE)
fit_data <- fit_plot_azimuthal(dtt_projected$azi_x,
                               dtt_projected$azi_y, 
                               z = dtt_projected$measurement,
                               outer_radius = 1.6,
                               spatial_res = 1000,
                               lambda = 0.01,
                               col_levels = 50,
                               contour_levels = 20,
                               extrapolate = FALSE,
                               compute_error = TRUE,
                               eye_diameter = 0,
                               axial_len = 0,
                               falciform_coords = NA)
polygon(falciform_dt$azi_x,falciform_dt$azi_y, col="black")
dev.off()
```

Evaluate error. [explain in more detail]

```{r, warning=FALSE}
plot(fit_data[[1]], show_boxplot=TRUE)
# plot_from_MAT_simpler(fit_data[[2]]$z) 
```

