---
title: "Retina Package"
author: "Brian Cohn"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Retina Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```
load_all()
source("3hgbqg" %>% path_to_main_file_for_test_retina)
retina_A <- main_3hgbqg("3hgbqg" %>% get_path_to_test_retina_folder)
source("40oik5" %>% path_to_main_file_for_test_retina)
retina_B <- main_40oik5("40oik5" %>% get_path_to_test_retina_folder)
source("gv3igs" %>% path_to_main_file_for_test_retina)
retina_C <- main_gv3igs("gv3igs" %>% get_path_to_test_retina_folder)

retinaplot(retina_A)
fit_plots(retina_A$fit_data1)
fit_plots(retina_B$fit_data1)
fit_plots(retina_C$fit_data1)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style


## Installation

```
install.packages(c("cairoDevice", "RGtk2"), type="source")
install.packages('devtools')
devtools::install_github('bc/retina')
```

## Retina Plot

```{r, fig.height=5, fig.show='hold', fig.width=7, results='hide'}
retina_A <- retina::banded_gecko()
retina::retinaplot(retina_A)
```

# Predicting Fit Error

```
par(mfrow=c(2,2))
retina::fit_plots(retina_A$fit_data1)
par(mfrow=c(1,1))
```